InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex
Split up Results and discussion and mention issue with typo processor (#58)
* started extract

* Split up Results and discussion and mention issue with typo processor

---------

Co-authored-by: LukasMueller3 <lukas.mueller@nc-online.de>

\section{Results + Discussion}
In the following section we take a look on the results of the aforementioned experiment.

Fig. \ref{fig:stable_diffusion} shows how the different processors and their combinations effect an image generated by the stable diffusion generator. The bars are structured in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and on the right is the umm-maybe evaluator respectively. The different colors represent the different outputs. Black symbolizes that the image before and after processing was detected as AI-generated. Grey shows that both are detected to be human made, whereas for red the process did the exact opposite of what it should do and fool the detector in a way that after processing it is seen as AI-generated whereas before as human made. Lastly the green bar does exactly what is desired, so it pictures AI-generated content, where the executed augmentation lead to the detector guessing it was human-made. \\
The data depicted in fig. \ref{fig:stable_diffusion} shows, that only the nahrawy evaluator fooled the detector the wrong way round, but it is also the only one with the output of 'human-human'. Compared to the Dall-E generator in fig. \ref{fig:dallE} the amount of right tricking is relatively low. There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'.
It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors. This can be seen as they solely achieve a great result as well as their combinations with other ones. It is also worth mentioning that these results are only achieved when using the nahrawy evaluator. Whereas resnet18, which can be seen in both figures, couldn't be tricked by any processor.

@@

In fig. \ref{fig:gpt2} the text processors are plotted. The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one. It is visible that the double-whitespace processor solely has little effect whereas in combination with the typo processor the result rises enormously. This is due to the typo processor since it alone also achieves great results. The radar evaluator only produces only black bars. 
Similar results can be seen in fig. \ref{fig:falcon} where radar just contains black bars and typo as well, as its combination with the roberta base evaluator achieves great results. The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.

>>>>

\section{Results}
In the following section we take a look on the results of the aforementioned experiment.

Fig. \ref{fig:stable_diffusion} shows how the different processors and their combinations effect an image generated by the stable diffusion generator. The bars are structured in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and on the right is the umm-maybe evaluator respectively. The different colors represent the different outputs. Black symbolizes that the image before and after processing was detected as AI-generated. Grey shows that both are detected to be human made, whereas for red the process did the exact opposite of what it should do and fool the detector in a way that after processing it is seen as AI-generated whereas before as human made. Lastly the green bar does exactly what is desired, so it pictures AI-generated content, where the executed augmentation lead to the detector guessing it was human-made.

The data depicted in fig. \ref{fig:stable_diffusion} shows, that only the nahrawy evaluator fooled the detector the wrong way round, but it is also the only one with the output of 'human-human'. Compared to the Dall-E generator in fig. \ref{fig:dallE} the amount of right tricking is relatively low. There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'.

@@

In fig. \ref{fig:gpt2} the text processors are plotted. The colors and the concept stay the same, the left bar is using the radar evaluator and the right one the roberta base one. It is visible that the double-whitespace processor solely has little effect whereas in combination with the typo processor the result rises enormously. This is due to the typo processor since it alone also achieves great results. The radar evaluator only results in black bars. The results of the translator processor are not shown, as the implementation raised several errors during the experiment, which makes the results not suited for comparison.

Similar results can be seen in fig. \ref{fig:falcon} where radar and typo just contain black bars, as its combination with the roberta base evaluator achieves great results. The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
